PubCrawl: A Publication Search Engine

### 2012-05-18 report/paper.tex
Reword for clarity/consistency

\begin{figure}[p]
\centering
\includegraphics[width=5in]{images/Relevance1}
\caption{Relevance of search results grouped as Highly Relevant, Moderately
  Relevant and Not Relevant.}
\label{relevance1}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=5in]{images/Relevance2}
\caption{Relevance ratio vs. Search Engines.}
\label{relevance2}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=5in]{images/Relevance3}
\caption{Quality Score.}
\label{relevance3}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=5in]{images/Rank}
\caption{Rank order of search engines (Higher score indicates better rank; scale of 5).}
\label{rank1}
\end{figure}

@@

Our preliminary user study only involved 4 topics and hence a larger study must
be undertaken to rigorously study the quality of results. We also observed
that: (1) quality of results depends heavily on the breadth of the search term
(a narrow search term produces better results), (2) ground truth wasn't always
clearly known, (3) ground-truth is subjective, (4) we had to discard a large
number of highly relevant but non-ACM publications. Furthermore, because we did
not have data for non-ACM papers citing ACM papers, our PageRank algorithm was
weaker compared to other search engines. However, our preliminary user study
shows that PubCrawl can find relevant documents and effectively trade off
PageRank and text indexing scores.

>>>>

\begin{figure}[p]
\centering
\includegraphics[width=5in]{images/Relevance1}
\caption{Relevance of search results across all topics}
\label{relevance1}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=5in]{images/Relevance2}
\caption{Relevance ratio for each search engine}
\label{relevance2}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=5in]{images/Relevance3}
\caption{Quality score for each search engine}
\label{relevance3}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=5in]{images/Rank}
\caption{Average ranking of search engines (higher score is better)}
\label{rank1}
\end{figure}

@@

Our preliminary user study only involved 4 topics and hence a larger study must
be undertaken to rigorously study the quality of results. We also observed
that: (1) quality of results depends heavily on the breadth of the search term
(a narrow search term produces better results), (2) ground truth wasn't always
clearly known, (3) ground-truth is subjective, (4) we had to discard a large
number of highly relevant but non-ACM publications. Furthermore, because we did
not have data for non-ACM papers citing ACM papers, our PageRank algorithm was
weaker compared to other search engines. However, we did show that PubCrawl can
find relevant documents and effectively trade off PageRank and text indexing
scores.
